An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-14 paper.tex
Proofed the participants section.

\section*{Participants}
%
The study was approved by the Institutional Review Board of Cleveland State
University (\# 29904-VAN-HS) and informed consent was obtained from all
participants.

Fifteen able bodied subjects including four females and eleven males with an
average age of $24\pm4$ years, height of $1.75\pm0.09$ m, mass of $74\pm13$ kg
participated in the study. The data has been anonymized with respect to the
participants' identities and a unique identification number was assigned to
each subject. A selection of the meta data collected for each subject is shown
in Table~\ref{tab:subjects}.
%
\begin{table*}
  \cprotect\caption{Information about the 15 participants. The final three
    columns give the trial numbers associated with each nominal treadmill
    speed. Additional trials with subject 0 are trials with no subject, i.e.
    unloaded trials that can be used for inertial compensation purposes, and are
    not shown in the table. Generated by \verb|src/subject_table.py|.}
  \centering
  \input{tables/subjects.tex}
  \label{tab:subjects}
\end{table*}

>>>>

\section*{Participants}
%
Fifteen able bodied subjects including four females and eleven males with an
average age of $24\pm4$ years, height of $1.75\pm0.09$ m, mass of $74\pm13$ kg
participated in the study. The study was approved by the Institutional Review
Board of Cleveland State University (\# 29904-VAN-HS) and informed consent was
obtained from all participants. The data has been anonymized with respect to the
participants' identities and a unique identification number was assigned to
each subject. A selection of the meta data collected for each subject is shown
in Table~\ref{tab:subjects}.
%
\begin{table*}
  \cprotect\caption{Information about the 15 participants. The final three
    columns give the trial numbers associated with each nominal treadmill
    speed. The measured mass is computed from the mean total vertical ground
    reaction force just after the calibration pose event, if possible.
    Additional trials found in the data set with a subject identification
    number 0 are trials with no subject, i.e.  unloaded trials that can be used
    for inertial compensation purposes, and are not shown in the table. Generated
    by \verb|src/subject_table.py|.}
  \centering
  \small
  \input{tables/subjects.tex}
  \label{tab:subjects}
\end{table*}
